On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-02-07 v-research_experiment-alpha.tex
conclude first draft sec 2.2.3 (vuln & defect)

The definition given by the MITRE in\autocite{MITRE2020CWEweakness} of
weakness is: ``Software weaknesses are errors that can lead to software
vulnerabilities. A software vulnerability, such as those enumerated on the
Common Vulnerabilities and Exposures (CVE) List, is a mistake in software that
can be directly used by a hacker to gain access to a system or network''.
The definition is circular if we interpret the word ``error'' and
``mistake'' with the same semantics: a weakness is an error that leads to a
vulnerability and a vulnerability is a mistake which, in turn, is a weakness.
The only difference (between weakness and vulnerability) seems to be
that one can consider weakness as a ground term and state that a
vulnerability is caused by a weakness, i.e. 
$\World,\Weakness\models\Diamond\Vulnerability$ where
$\Weakness,\Vulnerability$ are Regions of Weaknesses and Vulnerabilities (resp.);
accepting the hierarchy in the CWE\autocite{CWE} as a ground truth. 
Similarly, we consider the CVE\autocite{CVE} (a database of Vulnerability) 
or the CVE reported in the NVD as a ground truth.

\begin{definition}{\bf Region: Weakness and Vulnerability --}\label{def:weakness}
	A Region $\region\subseteq\agent$ of an agent
	$\agent\in\agentuniverse$ is defined as Weakness $\Weakness$ (i.e.
	representing a weakness introduced by the agent into any phase of
	production, e.g.  of the secure process development life-cycle, of any
	system or subsystem) iff there exists $\world\in\possibleworlds$ such
	that $\World,\Weakness\models\Diamond\exists\Weakness',\Vulnerability'.~
	\po{\Weakness'}{\Vulnerability'}$, where $\Weakness'\subseteq\Weakness$, and
	$\Vulnerability'\subseteq\Vulnerability$ is a Region of an agent $\agent'\in\agentuniverse$.
\end{definition}

@@

\begin{figure}[t]
	\centering
	\begin{subfigure}[b]{.5\textwidth}
		\centering
		\includegraphics[width=.7\textwidth]{rcc5_CWE-116.pdf}
		\caption{Representation with RCC5}
		\label{fig:rcc5_CWE-116}
	\end{subfigure}\begin{subfigure}[b]{.5\textwidth}
		\centering
		\includegraphics[width=.7\textwidth]{rcc8_CWE-116.pdf}
		\caption{Representation with RCC8}
		\label{fig:rcc8_CWE-116}
	\end{subfigure}
	\begin{subfigure}[b]{.5\textwidth}
		\centering
		\includegraphics[width=.7\textwidth]{rcc8_CWE-116.pdf}
		\caption{Representation in K-Modal Logic}
		\label{fig:KML_CWE-116}
	\end{subfigure}
	\caption{Relations between CWE-116 and correlated CVEs}
\end{figure}

@@

In our informal definition depicted in Figure~\ref{fig:safety-security}, a
Vulnerability is seen as a process through which an agent (i.e. Mankind)
generates an Incident, i.e.
Agent$\rightarrow$Vulnerability$\rightarrow$Exploit$\rightarrow$Attack$\rightarrow$Incident.
We describe processes, in our current formalization, in terms of the K-Modal
Structure in Definition~\ref{def:modalinterpretation} (i.e. in terms of
causality principle).

@@

>>>>

The definition given by the MITRE in\autocite{MITRE2020CWEweakness} of
weakness is: ``Software weaknesses are errors that can lead to software
vulnerabilities. A software vulnerability, such as those enumerated on the
Common Vulnerabilities and Exposures (CVE) List, is a mistake in software that
can be directly used by a hacker to gain access to a system or network''.
The definition is circular if we interpret the word ``error'' and
``mistake'' with the same semantics: a weakness is an error that leads to a
vulnerability and a vulnerability is a mistake which, in turn, is a weakness.
The only difference (between weakness and vulnerability) seems to be
that one can consider weakness as a ground term and state that a
vulnerability is caused by a weakness, i.e. 
$\World,\Weakness\models\Diamond\Vulnerability\wedge\Weakness$ where
$\Weakness,\Vulnerability$ are Regions of Weaknesses and Vulnerabilities (resp.);
accepting the hierarchy in the CWE\autocite{CWE} as a ground truth. 
Similarly, we consider the CVE\autocite{CVE} (a database of Vulnerability) 
or the CVE reported in the NVD as a ground truth.

\begin{definition}{\bf Region: Weakness and Vulnerability --}\label{def:weakness}
	A Region $\region\subseteq\agent$ of an agent
	$\agent\in\agentuniverse$, is defined as Weakness $\Weakness$ (i.e.
	representing a weakness introduced by the agent into any phase of
	production, e.g.  of the secure process development life-cycle, of any
	system or subsystem) iff there exists $\world\in\possibleworlds$ such
	that $\world,\Weakness\models\Diamond\exists\Weakness',\Vulnerability'.~
	\rcc(\Weakness',\Vulnerability')\wedge\neg\dr{\Weakness'}{\Vulnerability'}$, 
	where $\Weakness'\subseteq\Weakness$, and
	$\Vulnerability'\subseteq\Vulnerability$ is a Region of an agent $\agent'\in\agentuniverse$.
\end{definition}

@@

\begin{figure}[t]
	\centering
	\begin{subfigure}[b]{.5\textwidth}
		\centering
		\includegraphics[width=.7\textwidth]{rcc5_CWE-116.pdf}
		\caption{Representation with RCC5}
		\label{fig:rcc5_CWE-116}
	\end{subfigure}\begin{subfigure}[b]{.5\textwidth}
		\centering
		\includegraphics[width=.7\textwidth]{rcc8_CWE-116.pdf}
		\caption{Representation with RCC8}
		\label{fig:rcc8_CWE-116}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{KML_CWE-116.pdf}
		\caption{Representation in K-Modal Logic}
		\label{fig:KML_CWE-116}
	\end{subfigure}
	\caption{Relations between CWE-116 and correlated CVEs}
\end{figure}

@@

\subsubsection{Process: Incidents and Accidents}\label{sec:vulnerabilitydefect}
In our informal definition depicted in Figure~\ref{fig:safety-security}, a
Vulnerability is seen as a process through which an agent (i.e. Mankind)
generates an Incident, i.e.
Agent$\rightarrow$Vulnerability$\rightarrow$Exploit$\rightarrow$Attack$\rightarrow$Incident.
We describe processes, in our current formalization, in terms of the K-Modal
Structure in Definition~\ref{def:modalinterpretation} (i.e. in terms of
causality principle).

@@

\subsubsection{Region: Threat and Asset}\label{sec:vulnerabilitydefect}
